Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and interpolation-extrapolation capacity validation

### 2022-10-17 Article.tex
Two new paragraphs added to the intro part and one new ref in Biblio

\OP{You must add here two paragraphs concerning a brief introduction to the Hansel-Spittel and the PTM models.}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]
{Figures/ANN-scheme-2HL}
\caption{Multi-layer Artificial Neural Network architecture \cite{Pantale-2021}.}
\label{fig:ANN-scheme-2HL}
\end{figure}

>>>>

\textcolor{red}{Another model widely used in the Forge software is the model developed by Hansel and Spittel \cite{hensel1978kraft}, commonly known as the HS model, which is a thermo-visco-plastic model and whose formulation is a product of the dependent functions of three physical variables. Unlike the JC model, this formulation does not imply an independence of the three physical variables since they are determined simultaneously. This model is simple to use and has $8$ coefficients that are easy to determine. The limitation of this model is that it loses its accuracy in some cases when all $8$ parameters have to be used. Hence many works limit its use very often to $5$ or $6$ parameters. This has been verified in our study where the smallest error of the model is found with $5$ parameters}.

\textcolor{purple}{The fixed and few number of parameters imposed by each analytical model as presented above has both advantages and disadvantages. The advantages are related to the fact that the models have few parameters and are therefore easy to identify, but the disadvantage is when the model has to be applied to a different material than the one for which it was developed and in this case the model loses its performance as in the case of the HS model. To try to solve this problem P. Tize Mha \eal \cite{TizeMha-2022} proposed a formulation where the number of parameters is not known in advance. Indeed, the idea is to make an analytical model formulation flexible so that it can be adapted to a large number of materials. This formulation is based on MZA model and polynomial functions are used allowing to find its final form from the functions intrinsic to the model. Another way to describe the flow behavior of material is to use neural network tool due to its capacity to solve complex problems}.

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.7\columnwidth]
{Figures/ANN-scheme-2HL}
\caption{Multi-layer Artificial Neural Network architecture}
\label{fig:ANN-scheme-2HL}
\end{figure}
